\documentclass{letter}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{ragged2e}

\name{Chetan Vig}
\address{Edmonton, Alberta, Canada}
\email{cvig@ualberta.ca}
\phone{+1(365)883-2406}
\date{\today}

\begin{document}

\begin{letter}{Stellari Hiring Team\\
[Address not provided in job posting]}

\opening{Dear Stellari Hiring Team,}

I am writing to express my enthusiastic interest in the Junior Full Stack Developer (Part-time, Student Only) position at Stellari, as advertised in Edmonton, AB. As a Computer Science student at the University of Alberta, anticipated graduation in 2027, and a registered student for Winter 2026, I am eager to apply my skills and passion for full-stack development to contribute to the development of Koru. My experience aligns well with the requirements of this role, and I am confident I can quickly become a valuable asset to your team.

My project, Clubmate AI, demonstrates my ability to build and deploy full-stack applications. I developed an Async Python service bridging an LLM to execute API tools for server automation, implemented Role-Based Access Control using Discord roles, and enforced data reliability using Pydantic. The project reduced club administrative burden by an estimated 80%, showcasing my ability to deliver impactful solutions. I am proficient in JavaScript, React, Python, and have a strong understanding of REST APIs, SQL, and Git, skills directly applicable to the responsibilities outlined in the job description. I am also comfortable with Linux CLI, Docker, and have some experience with AWS, which I understand is an asset.

I am particularly drawn to Stellari's commitment to providing mentorship and a flexible work environment that supports students. I am a responsible, organized, and communicative individual, comfortable working independently in a remote setting. I am eager to learn new tools and technologies and contribute to the early stages of a new software product. The opportunity to gain practical experience in full-stack development, cloud technologies, and agile workflows, while contributing to a real production application, is incredibly appealing.

Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss my qualifications further.

\closing{Sincerely,}

\signature{Chetan Vig}

\end{letter}

\end{document}