\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{geometry}
\geometry{left=0.75in,top=0.75in,right=0.75in,bottom=0.75in}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, citecolor=blue}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

\begin{document}

\input{glyphtounicode}
\pdfgentounicode=1

%---------- CONTACT INFORMATION ----------
\begin{center}
    {\LARGE \textbf{Chetan Vig}} \\
    \vspace{1mm}
    Edmonton, Alberta, Canada \\
    \href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} $|$ +1(365)883-2406 $|$ \href{https://github.com/vigchetan}{github.com/vigchetan}
\end{center}

%---------- PROFESSIONAL SUMMARY ----------
\section*{\textbf{Summary}}
Highly motivated Computer Science student at the University of Alberta seeking a Junior Full Stack Developer internship at Stellari.  Experienced in building AI-powered applications with Python, JavaScript, React, and REST APIs. Eager to contribute to the development of Koru, leveraging skills in full-stack development and cloud technologies while learning from experienced professionals in an agile environment.  Registered student for Winter 2026.

%---------- EXPERIENCE ----------
\section*{\textbf{Experience}}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt]
    \item \textbf{MacEwan Residence} \hfill \textit{MacEwan University, Edmonton, Alberta} \hfill \textit{November 2024 - Present}
    \begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=0pt]
        \item Provided excellent customer service to students and guests, handling check-ins, check-outs, and inquiries.
        \item Maintained organized records, managed mail and packages, and assisted with administrative tasks.
        \item Facilitated seamless guest and student experiences by efficiently addressing inquiries and coordinating check-ins and check-outs.
    \end{itemize}
\end{itemize}

%---------- PROJECTS ----------
\section*{\textbf{Projects}}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt]
    \item \textbf{Clubmate AI - Ongoing} \hfill \textit{Undergraduate Artificial Intelligence Society, github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI} \hfill \textit{September 2025 - Present}
    \begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=0pt]
        \item \textbf{Technologies:} Python, MCP SDK, LLMs (OpenAI standard), Pydantic, Async/Await.
        \item Developed a high-performance, Async Python service bridging an LLM via Model Context Protocol (MCP) to execute 17 standardized API tools for server automation.
        \item Implemented strict Role-Based Access Control (RBAC) using Discord roles for tool permissions, and enforced data reliability across all inputs using Pydantic schema validation.
        \item Reduced club administrative burden by an estimated 80\% (scheduling, moderation, outreach), freeing leadership time and measurably increasing member engagement.
    \end{itemize}
\end{itemize}

%---------- INVOLVEMENT ----------
\section*{\textbf{Involvement}}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt]
    \item \textbf{Perplexity} \hfill \textit{Edmonton, Alberta} \hfill \textit{September 2025 - Present}
    \begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=0pt]
        \item Promoted Perplexity's Comet browser on campus through creative grassroots events and outreach.
        \item Collaborated with the growth team and student strategists to boost awareness and signups, distributed branded materials, and gathered feedback.
        \item Developed marketing and communication skills in a fast-paced, tech-driven environment.
    \end{itemize}
\end{itemize}

%---------- EDUCATION ----------
\section*{\textbf{Education}}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt]
    \item \textbf{University of Alberta} \hfill \textit{Edmonton, Alberta} \hfill \textit{2027}
    \begin{itemize}[leftmargin=0.15in, itemsep=2pt, parsep=0pt]
        \item Bachelor of Science, Computer Science (Expected)
    \end{itemize}
\end{itemize}

%---------- SKILLS ----------
\section*{\textbf{Skills}}
\begin{itemize}[leftmargin=0.2in, itemsep=2pt, parsep=0pt]
    \item \textbf{Full Stack Development:} JavaScript/TypeScript, React, REST APIs, Node.js, HTML/CSS, Git, GitHub, Agile/Kanban workflow
    \item \textbf{Programming & CS:} Python, C (C99), SQL, data structures & algorithms, OOP, spec-driven development
    \item \textbf{AI / ML & Data:} Machine learning & deep learning, LLMs & context engineering, RAG, PyTorch, Scikit-Learn, NumPy, Pandas, Seaborn, LangChain, LlamaIndex, Pinecone, Hugging Face, SpaCy, data analysis & visualization, feature engineering, hypothesis testing
    \item \textbf{Systems, Web & Tools:} PostgreSQL, Linux CLI, Docker, Streamlit, PyTest, MCP / MCP SDK, AWS (learning), Tailwind CSS
\end{itemize}

\end{document}