\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\usepackage{hyperref}

\begin{document}

\begin{letter}{CGI Hiring Team\\
[Address Redacted for Privacy]} % Replace with actual address if available

\opening{Dear CGI Hiring Team,}

I am writing to express my keen interest in the Generative AI Developer position at CGI in Edmonton, Alberta. As a Computer Science student at the University of Alberta with a strong focus on AI/ML and practical application development, I am confident that my skills and experience align well with the requirements outlined in the job description.

My passion for generative AI is demonstrated through my project, Clubmate AI, where I developed an LLM-based system using Python, OpenAI APIs, and Pydantic for data validation. This project involved prompt engineering, model integration via the Model Context Protocol (MCP), and the implementation of Role-Based Access Control (RBAC) for security. I successfully reduced the club's administrative burden by an estimated 80%, measurably increasing member engagement. This experience directly relates to the duties mentioned in the job description, including prompt refinement, model tuning, and the integration of AI models into applications.

I also have experience with enterprise web app development, and I am familiar with frameworks like LangChain. My proficiency in Python, coupled with my knowledge of machine learning concepts, including fine-tuning, positions me well to contribute to CGI's AI capabilities. Furthermore, my involvement with Perplexity has honed my communication skills, enabling me to effectively explain AI behavior and constraints to cross-functional teams.

Thank you for considering my application. I am eager to learn more about this opportunity and discuss how my skills and enthusiasm can contribute to CGI's success.

\closing{Sincerely,}

\vspace{0.5cm}
Chetan Vig\\
\href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} \\
+1(365)883-2406 \\
\href{https://github.com/vigchetan}{github.com/vigchetan}

\end{letter}

\end{document}