\documentclass[letterpaper,11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{ragged2e}

\renewcommand{\familydefault}{\sfdefault}

\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,
    urlcolor=blue,
}

\newcommand{\tightlist}{
    \setlength{\itemsep}{1pt}
    \setlength{\parskip}{0pt}
}

\newenvironment{tightitemize}
{\begin{itemize}[nosep,topsep=0pt,parsep=0pt,partopsep=0pt]}{\end{itemize}}

\begin{document}

\begin{center}
{\LARGE \textbf{Chetan Vig}} \\
\vspace{0.05in}
Edmonton, Alberta, Canada | \href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} | +1(365)883-2406 | \href{https://github.com/vigchetan}{github.com/vigchetan}
\end{center}

\vspace{0.1in}

\section*{\textbf{Summary}}
Highly motivated Computer Science student at the University of Alberta with experience in developing AI-powered applications, particularly in the realm of generative AI. Currently building an LLM-based assistant using Python, APIs, and databases. Eager to apply expertise in prompt engineering, model optimization, and AI integration to contribute to innovative projects as a Generative AI Developer at CGI. Seeking an internship opportunity to leverage skills in AI/ML, web application development, and problem-solving to enhance AI capabilities and drive organizational goals.

\vspace{0.1in}

\section*{\textbf{Skills}}

\noindent\textbf{AI / ML \& Data:} Machine learning & deep learning, LLMs & context engineering, RAG, Prompt Engineering, Model Fine-tuning, PyTorch, Scikit-Learn, NumPy, Pandas, Seaborn, LangChain, LlamaIndex, Pinecone, Hugging Face, SpaCy, data analysis & visualization, feature engineering, hypothesis testing.

\noindent\textbf{Programming \& CS:} Python, C (C99), JavaScript/TypeScript, SQL, data structures & algorithms, OOP, spec-driven development.

\noindent\textbf{Systems, Web \& Tools:} React, REST APIs, PostgreSQL, Git, Linux CLI, Docker, Streamlit, PyTest, MCP / MCP SDK, AWS (learning).

\vspace{0.1in}

\section*{\textbf{Projects}}

\noindent\textbf{Clubmate AI - Ongoing} \hfill September 2025 - Present\\
\textit{Undergraduate Artificial Intelligence Society} \href{https://github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI}{(github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI)}\\
\begin{tightitemize}
    \item Developed a high-performance, Async Python service bridging an LLM (OpenAI standard) via Model Context Protocol (MCP) to execute 17 standardized API tools for server automation, demonstrating strong integration of LLMs and API tools.
    \item Implemented strict Role-Based Access Control (RBAC) using Discord roles for tool permissions, and enforced data reliability across all inputs using Pydantic schema validation, showcasing expertise in security and data validation.
    \item Reduced club administrative burden by an estimated 80% (scheduling, moderation, outreach), freeing leadership time and measurably increasing member engagement, quantifying the impact of AI-driven solutions.
    \item \textbf{Technologies:} Python, MCP SDK, LLMs (OpenAI standard), Pydantic, Async/Await.
\end{tightitemize}

\vspace{0.1in}

\section*{\textbf{Experience}}

\noindent\textbf{MacEwan Residence} \hfill November 2024 - Present\\
\textit{MacEwan University, Edmonton, Alberta}\\
\begin{tightitemize}
    \item Provided excellent customer service for students and guests, handling check-ins, check-outs, and inquiries, demonstrating strong communication and problem-solving skills.
    \item Maintained organized records, managed mail and packages, and assisted with administrative tasks.
    \item Facilitated seamless guest and student experiences by efficiently addressing inquiries, coordinating check-ins and check-outs.
\end{tightitemize}

\vspace{0.1in}

\noindent\textbf{INVOLVEMENT} \hfill September 2025 - Present\\
\textit{Perplexity, Edmonton, Alberta}\\
\begin{tightitemize}
    \item Promoted Perplexity's Comet browser on campus through creative grassroots events and outreach.
    \item Collaborated with the growth team and student strategists to boost awareness and signups, distributed branded materials, and gathered feedback.
    \item Developed marketing and communication skills in a fast-paced, tech-driven environment.
\end{tightitemize}

\vspace{0.1in}

\section*{\textbf{Education}}

\noindent\textbf{University of Alberta} \hfill 2027 (Expected)\\
Edmonton, Alberta

\end{document}