\documentclass{letter}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{lipsum}

\begin{document}

\begin{letter}{Amazon Recruiting Team\\ Vancouver, BC}

\opening{Dear Amazon Recruiting Team,}

I am writing to express my enthusiastic interest in the Software Development Engineer Internship - Summer 2026 (Canada) position in Vancouver, BC. As a Computer Science student at the University of Alberta with a passion for building AI-powered applications and a strong foundation in software development, I am confident that my skills and experience align well with the requirements of this role and Amazon's commitment to innovation and customer obsession.

My project, Clubmate AI, demonstrates my ability to leverage modern technologies to solve real-world problems. I developed an Async Python service that integrates an LLM with standardized API tools for Discord server automation. This involved implementing Role-Based Access Control for security and Pydantic schema validation for data reliability. The project resulted in an estimated 80\% reduction in administrative burden, showcasing my ability to design, develop, and deploy impactful solutions. Furthermore, my involvement with Perplexity has honed my marketing and communication skills in a fast-paced tech environment.

My proficiency in Python, data structures, and algorithms, coupled with my experience in AI/ML technologies such as LLMs, PyTorch, and LangChain, makes me well-equipped to contribute to Amazon's innovative projects. I am also familiar with cloud-native architectures, REST APIs, and tools like Docker and Git. I am eager to learn and adapt to new technologies quickly, and I am particularly interested in leveraging GenAI and AI-powered tools to enhance development productivity, as highlighted in the job description. I am excited by the opportunity to contribute to a company that values ownership and operational excellence.

Thank you for considering my application. I am eager to learn more about this opportunity and discuss how my skills and passion can contribute to Amazon's success. My resume, which is attached, provides further detail on my qualifications.

\closing{Sincerely,}

\vspace{0.5cm}
Chetan Vig\\
\href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} \\
+1(365)883-2406 \\
\href{https://github.com/vigchetan}{github.com/vigchetan}
\end{letter}

\end{document}