\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\usepackage[margin=0.75in]{geometry}

% Define colors
\definecolor{darkgray}{rgb}{0.3,0.3,0.3}
\definecolor{lightgray}{rgb}{0.9,0.9,0.9}

% Custom commands
\newcommand{\resheading}[1]{\vspace{2mm}\noindent\textbf{#1}}
\newcommand{\resitem}[1]{\item #1 \vspace{-2pt}}
\newcommand{\skill}[1]{\texttt{#1}}

% Section formatting
\titleformat{\section}{
  \bfseries\scshape\Large
}{}{0em}{}

%-------------------------
% CONTACT INFORMATION
%-------------------------
\begin{document}

\begin{center}
    {\Huge \scshape Chetan Vig} \\
    \vspace{1mm}
    \small
    \href{mailto:cvig@ualberta.ca}{\texttt{cvig@ualberta.ca}} $|$
    +1(365)883-2406 $|$
    Edmonton, Alberta, Canada $|$
    \href{https://github.com/vigchetan}{\texttt{github.com/vigchetan}}
\end{center}

%-------------------------
% SUMMARY
%-------------------------
\section{Summary}
Highly motivated Computer Science student at the University of Alberta seeking a Software Development Engineer Internship at Amazon. Proven ability to design, develop, and deploy innovative solutions using modern technologies, including AI/ML and cloud-native architectures. Passionate about building scalable and resilient systems that solve real-world problems and impact millions of users. Eager to contribute to a collaborative team environment and learn from experienced engineers.

%-------------------------
% EXPERIENCE
%-------------------------
\section{Experience}

\noindent\textbf{MacEwan Residence - MacEwan University} \hfill Edmonton, Alberta \\
\noindent\textit{MacEwan Residence} \hfill November 2024 – Present
\begin{itemize}[leftmargin=0.2in, itemsep=1pt, parsep=0pt]
    \resitem{Provided excellent customer service to students and guests, efficiently handling check-ins, check-outs, and inquiries.}
    \resitem{Maintained organized records, managed mail and packages, and assisted with administrative tasks.}
    \resitem{Facilitated seamless guest and student experiences by efficiently addressing inquiries and coordinating check-ins and check-outs.}
\end{itemize}

%-------------------------
% PROJECTS
%-------------------------
\section{Projects}

\noindent\textbf{Clubmate AI - Ongoing} \hfill September 2025 – Present \\
\noindent\textit{Undergraduate Artificial Intelligence Society} \hfill \href{https://github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI}{\texttt{github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI}}
\begin{itemize}[leftmargin=0.2in, itemsep=1pt, parsep=0pt]
    \resitem{\textbf{LLM & Protocol Integration:} Developed a high-performance, Async Python service bridging an LLM via Model Context Protocol (MCP) to execute 17 standardized API tools for server automation, enhancing development productivity.}
    \resitem{\textbf{Security & Validation:} Implemented strict Role-Based Access Control (RBAC) using Discord roles for tool permissions, and enforced data reliability across all inputs using Pydantic schema validation.}
    \resitem{\textbf{Quantified Impact:} Reduced club administrative burden by an estimated 80\% (scheduling, moderation, outreach), freeing leadership time and measurably increasing member engagement.}
    \resitem{Utilized technologies including Python, MCP SDK, LLMs (OpenAI standard), Pydantic, and Async/Await.}
\end{itemize}

%-------------------------
% EDUCATION
%-------------------------
\section{Education}

\noindent\textbf{University of Alberta} \hfill Edmonton, Alberta \\
\noindent\textit{Bachelor of Science in Computer Science} \hfill Expected Graduation: 2027

%-------------------------
% SKILLS
%-------------------------
\section{Skills}

\noindent\textbf{Programming Languages:} Python, C (C99), JavaScript/TypeScript, SQL \\
\noindent\textbf{AI/ML \& Data:} Machine learning, deep learning, LLMs, context engineering, RAG, PyTorch, Scikit-Learn, NumPy, Pandas, LangChain, LlamaIndex, data analysis & visualization \\
\noindent\textbf{Systems, Web \& Tools:} React, REST APIs, PostgreSQL, Git, Linux CLI, Docker, Streamlit, PyTest, MCP / MCP SDK, AWS (learning), CI/CD principles

%-------------------------
% VOLUNTEER EXPERIENCE
%-------------------------
\section{Volunteer Experience}

\noindent\textbf{Perplexity} \hfill Edmonton, Alberta \\
\noindent\textit{Campus Ambassador} \hfill September 2025 – Present
\begin{itemize}[leftmargin=0.2in, itemsep=1pt, parsep=0pt]
    \resitem{Promoted Perplexity's Comet browser on campus through creative grassroots events and outreach.}
    \resitem{Collaborated with the growth team to boost awareness and signups, distributed branded materials, and gathered feedback.}
    \resitem{Developed marketing and communication skills in a fast-paced, tech-driven environment.}
\end{itemize}

\end{document}