\documentclass{letter}
\usepackage{geometry}
\geometry{a4paper, margin=1in}
\usepackage{hyperref}
\usepackage{lipsum}

\begin{document}

\begin{letter}{}

\opening{Dear Hiring Manager,}

I am writing to express my enthusiastic interest in the Marketing Front-End AI Co-op position at Revvity, as advertised. As a Computer Science student at the University of Alberta with a strong focus on AI/ML and front-end development, I am confident that my skills and experience align perfectly with the requirements of this role.

My passion for leveraging AI to enhance user experiences is demonstrated by my project, Clubmate AI, where I developed an LLM-based system using Python, MCP SDK, and OpenAI APIs to automate Discord workflows. This project involved integrating AI-powered features, similar to the chatbot and content recommendation systems mentioned in the job description. Furthermore, I have hands-on experience with front-end frameworks like React, essential for developing user-facing features using HTML, CSS, and JavaScript. My GitHub profile (\href{https://github.com/vigchetan}{github.com/vigchetan}) showcases these projects.

I am eager to contribute to Revvity Signals by building responsive and accessible user interfaces, utilizing AI coding assistants like GitHub Copilot to accelerate development, and optimizing AI tool outputs through prompt engineering. My experience with Git for version control, understanding of REST APIs, and familiarity with AI/ML concepts make me a strong candidate for this position. I am particularly excited about the opportunity to learn from experienced developers and gain hands-on experience with production AI implementations in a B2B SaaS environment.

Thank you for considering my application. I am available for an interview at your earliest convenience and look forward to discussing how my skills and enthusiasm can benefit Revvity.

\closing{Sincerely,}

\vspace{0.5cm}
Chetan Vig \\
\href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} \\
+1(365)883-2406 \\
\href{https://github.com/vigchetan}{github.com/vigchetan}
\end{letter}

\end{document}