\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{geometry}
\geometry{left=0.75in,top=0.75in,right=0.75in,bottom=0.75in}
\usepackage{enumitem}
\usepackage{ragged2e}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{url}
\usepackage{hyperref}
\hypersetup{colorlinks=true, linkcolor=blue, urlcolor=blue}

\urlstyle{same}

\raggedright
\setlength{\tabcolsep}{0in}

\begin{document}

\input{glyphtounicode}
\pdfgentounicode=1

%---------- TITLE ----------
\begin{center}
    {\Huge \textbf{Chetan Vig}} \\
    \vspace{0.5mm}
    Edmonton, Alberta, Canada \\
    \href{mailto:cvig@ualberta.ca}{cvig@ualberta.ca} $|$ +1(365)883-2406 $|$ \href{https://github.com/vigchetan}{github.com/vigchetan}
\end{center}

%---------- SUMMARY ----------
\section*{}
\noindent
Highly motivated Computer Science student at the University of Alberta with experience in front-end development and AI/ML integration.  Passionate about leveraging AI tools to enhance user experiences and streamline development workflows. Seeking a Marketing Front-End AI Co-op position at Revvity to contribute to building innovative and accessible web applications.

%---------- SKILLS ----------
\section*{}
\noindent
\textbf{Skills} \\
\begin{itemize}[leftmargin=*, nosep]
    \item \textbf{Front-End Development:} HTML, CSS, JavaScript, React, REST APIs, Responsive Design, Cross-Browser Compatibility
    \item \textbf{AI/ML:} LLMs & Context Engineering, RAG, Prompt Engineering, Integration of AI Services (Chatbots, Content Generation), AI Accessibility Considerations
    \item \textbf{AI Tools:} GitHub Copilot, ChatGPT, Claude, MCP / MCP SDK
    \item \textbf{Programming:} Python, C (C99), TypeScript, SQL, Data Structures & Algorithms, OOP
    \item \textbf{Tools \& Technologies:} Git, Linux CLI, Docker, Streamlit, PyTest, PostgreSQL, AWS (learning)
\end{itemize}

%---------- EXPERIENCE ----------
\section*{}
\noindent
\textbf{Experience} \\

\noindent\textbf{MacEwan Residence - MacEwan University} \hfill Edmonton, Alberta \\
\textit{MacEwan Residence} \hfill November 2024 – Present
\begin{itemize}[leftmargin=*, nosep]
    \item Provided customer service for students and guests, handling check-ins, check-outs, and inquiries.
    \item Maintained organized records, managed mail and packages, and assisted with administrative tasks.
    \item Facilitated seamless guest and student experiences by efficiently addressing inquiries and coordinating check-ins and check-outs.
\end{itemize}

%---------- PROJECTS ----------
\section*{}
\noindent
\textbf{Projects} \\

\noindent\textbf{Clubmate AI - Ongoing} \hfill September 2025 – Present \\
\textit{Undergraduate Artificial Intelligence Society} $|$ \href{https://github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI}{github.com/UndergraduateArtificialIntelligenceClub/Clubmate-AI}
\begin{itemize}[leftmargin=*, nosep]
    \item Developed an Async Python service bridging an LLM via Model Context Protocol (MCP) to execute 17 standardized API tools for server automation, enhancing web application capabilities.
    \item Implemented strict Role-Based Access Control (RBAC) using Discord roles for tool permissions, ensuring data reliability across all inputs using Pydantic schema validation.
    \item Reduced club administrative burden by an estimated 80\% (scheduling, moderation, outreach) using AI-driven automation, freeing leadership time and measurably increasing member engagement.
    \item Technologies: Python, MCP SDK, LLMs (OpenAI standard), Pydantic, Async/Await
\end{itemize}

%---------- INVOLVEMENT ----------
\section*{}
\noindent
\textbf{Involvement} \\

\noindent\textbf{Perplexity} \hfill Edmonton, Alberta \\
\textit{INVOLVEMENT} \hfill September 2025 – Present
\begin{itemize}[leftmargin=*, nosep]
    \item Promoted Perplexity's Comet browser on campus through creative grassroots events and outreach.
    \item Collaborated with the growth team and student strategists to boost awareness and signups, distributed branded materials, and gathered feedback.
    \item Developed marketing and communication skills in a fast-paced, tech-driven environment.
\end{itemize}

%---------- EDUCATION ----------
\section*{}
\noindent
\textbf{Education} \\

\noindent\textbf{University of Alberta} \hfill Edmonton, Alberta \\
Bachelor of Science, Computer Science \hfill Expected 2027

\end{document}