\documentclass{letter}
\usepackage{geometry}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\usepackage{hyperref}

\begin{document}

\begin{letter}{Hiring Manager\\Clio\\Calgary, AB}

\opening{Dear Hiring Manager,}

I am writing to express my enthusiastic interest in the Co-op Software Engineer position at Clio, as advertised. As a Computer Science student at the University of Alberta, currently entering my third year, I am confident that my skills and experience align well with the requirements outlined in the job description. I am particularly drawn to Clio's commitment to building next-gen SaaS solutions within the legal technology space.

My coursework has provided me with a solid foundation in computer science fundamentals, including data structures, algorithms, and SQL, as demonstrated by the skills listed in my resume. Beyond academics, I have actively sought opportunities to apply these skills in practical projects. For instance, I am currently developing Clubmate AI, an LLM-based club assistant using Python, APIs, and databases, which showcases my ability to design, develop, and deploy software solutions. This project also highlights my proficiency in technologies such as Python, REST APIs, and Git, all of which I believe would be valuable assets to your team.

Furthermore, my experience at MacEwan Residence has honed my communication and customer service skills, allowing me to effectively collaborate and address inquiries. I am eager to contribute to technical scoping and planning, communicate project progress effectively, and work collaboratively within a team at Clio. Thank you for considering my application. I have attached my resume for your review and welcome the opportunity to discuss my qualifications further in an interview.

\closing{Sincerely,}

\signature{Chetan Vig}
\vspace{0.5cm}
\hspace{0cm} \texttt{cvig@ualberta.ca} \\
\hspace{0cm} +1(365)883-2406 \\
\hspace{0cm} \href{github.com/vigchetan}{github.com/vigchetan}

\end{letter}

\end{document}