\documentclass[letterpaper, 11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{ragged2e}

\usepackage{geometry}
\geometry{
  left=0.75in,
  top=0.75in,
  right=0.75in,
  bottom=0.75in
}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\setlength{\oddsidemargin}{0in}
\setlength{\evensidemargin}{0in}
\setlength{\textwidth}{6.5in}
\setlength{\topmargin}{-.5in}
\setlength{\textheight}{9in}

\urlstyle{same}

\raggedright
\frenchspacing

% Define custom colors
\definecolor{darkgray}{rgb}{0.3,0.3,0.3}
\definecolor{lightgray}{rgb}{0.9,0.9,0.9}

% Define section formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Define itemize environment
\newenvironment{itemize*}%
  {\begin{itemize}[leftmargin=1.5em]}%
  {\end{itemize}}

% Define enumerate environment
\newenvironment{enumerate*}%
  {\begin{enumerate}[leftmargin=1.5em]}%
  {\end{enumerate}}

% Define command for skills
\newcommand{\skills}[1]{\noindent{\textbf{Skills:}} #1}

% Define command for experience
\newcommand{\experience}[4]{
  \textbf{#1} \\
  \textit{#2} \\
  \textit{#3 -- #4}
}

% Define command for project
\newcommand{\project}[3]{
  \textbf{#1} \\
  \textit{#2} \\
  \textit{#3}
}

\begin{document}

% Header
\begin{center}
  {\Huge \scshape Chetan Vig} \\
  \vspace{1pt}
  Edmonton, Alberta, Canada \hspace{20pt}
  \href{mailto:cvig@ualberta.ca}{\underline{cvig@ualberta.ca}} \hspace{20pt}
  +1(365)883-2406 \hspace{20pt}
  \href{https://github.com/vigchetan}{\underline{github.com/vigchetan}}
\end{center}

% Summary
\section{Summary}
Highly motivated Computer Science student at the University of Alberta with a strong foundation in data structures, algorithms, and software development.  Experienced in building AI-powered applications using Python and modern development tools. Seeking a Co-op Software Engineer position at Clio to contribute to the design, development, and deployment of high-quality software. Eager to apply strong communication and problem-solving skills in a collaborative, hybrid work environment.

% Education
\section{Education}
\textbf{University of Alberta} \hfill 2027 \\
Edmonton, Alberta

% Experience
\section{Experience}

\textbf{MacEwan Residence} \hfill November 2024 -- Present \\
\textit{MacEwan University} \hfill Edmonton, Alberta
\begin{itemize*}
    \item Provided excellent customer service to students and guests, handling inquiries and facilitating check-ins/check-outs.
    \item Maintained organized records and assisted with administrative tasks.
\end{itemize*}

% Projects
\section{Projects}

\textbf{Clubmate AI} \hfill September 2025 -- Present \\
\textit{Undergraduate Artificial Intelligence Society}
\begin{itemize*}
    \item \textbf{LLM \& Protocol Integration:} Developed a high-performance, Async Python service bridging an LLM via Model Context Protocol (MCP) to execute 17 standardized API tools for server automation.
    \item \textbf{Security \& Validation:} Implemented strict Role-Based Access Control (RBAC) using Discord roles for tool permissions, and enforced data reliability across all inputs using Pydantic schema validation.
    \item \textbf{Quantified Impact:} Reduced club administrative burden by an estimated 80\% (scheduling, moderation, outreach), freeing leadership time and measurably increasing member engagement.
    \item \textit{Technologies: Python, MCP SDK, LLMs (OpenAI standard), Pydantic, Async/Await}
\end{itemize*}

% Skills
\section{Skills}

\textbf{Programming Languages:} Python, C (C99), JavaScript/TypeScript, SQL

\textbf{Data Structures \& Algorithms:} Proficient in fundamental data structures and algorithms.

\textbf{AI/ML \& Data:} Machine learning & deep learning, LLMs & context engineering, RAG, PyTorch, Scikit-Learn, NumPy, Pandas

\textbf{Web \& Tools:} React, REST APIs, PostgreSQL, Git, Linux CLI, Docker, Streamlit, PyTest

\textbf{Other:} OOP, Spec-driven development, Data Analysis & Visualization, Critical Thinking, Communication Skills.

% Involvement
\section{Involvement}

\textbf{Perplexity} \hfill September 2025 -- Present \\
Edmonton, Alberta
\begin{itemize*}
    \item Promoted Perplexity's Comet browser on campus through creative grassroots events and outreach.
    \item Collaborated with the growth team and student strategists to boost awareness and signups.
    \item Developed marketing and communication skills in a fast-paced, tech-driven environment.
\end{itemize*}

\end{document}